---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
activity <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
activityPerDay <- with(activity, aggregate(steps,
            by=list(date=date), FUN=function(x) { mean(x, na.rm=T) }))
hist(activityPerDay$x)
mean(activityPerDay$x, na.rm=T)
median(activityPerDay$x, na.rm=T)
```

## What is the average daily activity pattern?

```{r}
activityPerInterval <- with(activity, aggregate(steps,
            by=list(interval=interval), FUN=function(x) { mean(x, na.rm=T) }))
with(activityPerInterval, plot(interval, x, type="l"))
```

The interval with the greatest activity is:

```{r}
activityPerInterval$interval[which.max(activityPerInterval$x)]
```

## Imputing missing values

Let's see the number of missing values:

```{r}
sum(is.na(activity$steps))
```

We replace the missing values by the mean of the closest previous measure and
the closest next measure:

```{r}
activity$steps2 <- activity$steps
for (i in 1:length(activity$steps2))
    if (is.na(activity$steps2[i])) {
        before <- rev(which(!is.na(activity$steps[1:i])))[1]
        after <- which(!is.na(activity$steps[-(1:i)]))[1] + i
        if (!is.na(before) & !is.na(after)) {
            activity$steps2[i] <- (activity$steps2[before] + activity$steps2[after]) / 2
        } else if (!is.na(before)) {
            activity$steps2[i] <- activity$steps2[before]
        } else {
            activity$steps2[i] <- activity$steps2[after]
        }
    }
```

Let's redo the first part of this analysis:

```{r}
activityPerDay <- with(activity, aggregate(steps2, by=list(date=date), FUN=mean))
hist(activityPerDay$x)
mean(activityPerDay$x)
median(activityPerDay$x)
```

Most missing values have been replaced by 0. The mean and median are thus lower.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
activity$day <- weekdays(strptime(activity$date, "%Y-%m-%d"))
activity$day <- with(activity, replace(day, day == "samedi" | day == "dimanche", "weekend"))
activity$day <- with(activity, replace(day, day != "weekend", "weekday"))
activity$day <- factor(activity$day)
library(ggplot2)
p <- ggplot(activity, aes(x=interval, y=steps2))
p <- p + stat_summary(fun.y="sum", geom="line")
p <- p + facet_grid(day ~ .)
print(p)
```
